---
title: "ABM4_Kwon_YoungJu"
author: "kwon"
date: "2018년 11월 1일"
output: 
  pdf_document: 
    keep_tex: no
    latex_engine: xelatex
---

# Assignment 4

##*(a)*
```{r a}
data = read.table("hubbledata.txt", header=T)
plot(data$distance, data$radialvelocity, xlab= "distance", ylab= "radial velocity", main="Hubble")
```

##*(b)*
###*(i)*
```{r bi}
# jags model
# model {
# 
#   for (j in 1:length(radialvelocity)) {
#     radialvelocity[j] ~ dnorm(beta1+beta2*distance[j], sigmasqinv)
#   }
#   
#   beta1 ~ dnorm(0, 0.00000001)
#   beta2 ~ dnorm(0, 0.00000001)
#   sigmasqinv ~ dgamma(0.0001, 0.0001)
#   
#   sigmasq = 1/sigmasqinv
# }


require(rjags)
initial.vals = list(list(beta1 = 10000, beta2=10000, sigmasqinv=0.01),
                    list(beta1 = 10000, beta2=-10000, sigmasqinv=0.01),
                    list(beta1 = 10000, beta2=10000, sigmasqinv=0.000001),
                    list(beta1 = 10000, beta2=-10000, sigmasqinv=0.000001),
                    list(beta1 = -10000, beta2=10000, sigmasqinv=0.01),
                    list(beta1 = -10000, beta2=-10000, sigmasqinv=0.01),
                    list(beta1 = -10000, beta2=10000, sigmasqinv=0.000001),
                    list(beta1 = -10000, beta2=-10000, sigmasqinv=0.000001))
m1 = jags.model("hubble.bug", data, initial.vals, n.chains = 8)

update(m1, 2000)
x1 = coda.samples(m1, c("beta1", "beta2", "sigmasq"), n.iter=2000)
plot(x1, smooth = FALSE)
```
The classical linear regression gives 400 as slope, thus initial values of beta2 is set from -10000 to +10000.
For residual standard error, it gives 230. In similar context, the initial values for sigmasq is set from 100 to 1000000. \
As seen in the graph, trace of sigmasq, beta1, and beta2 overlap over all iterations. Moreover, density plot of three variables also look proper. \

###*(ii)*
```{r bii}
summary(x1)
```

###*(iii)*
```{r biii}
post.samp = as.matrix(x1)
mean(post.samp[, "beta2"])
quantile(post.samp[,"beta2"], c(0.025, 0.975))
```
Mean and 95% posterior credible interval of slope appear to be positive.

###*(iv)*
```{r biv}
mean(post.samp[, "beta1"])
quantile(post.samp[,"beta1"], c(0.025, 0.975))
```
Posterior credible interval of intercept contains zero.

##*(c)*
###*(i)*
```{r ci}
# jags model2
# model {
# 
#   for (j in 1:length(radialvelocity)) {
#     radialvelocity[j] ~ dnorm(beta2*distance[j], sigmasqinv)
#   }
#   
#   beta2 ~ dnorm(0, 0.00000001)
#   sigmasqinv ~ dgamma(0.0001, 0.0001)
#   
#   sigmasq = 1/sigmasqinv
# }

initial.vals = list(list(beta2=10000, sigmasqinv=0.01),
                    list(beta2=-10000, sigmasqinv=0.01),
                    list(beta2=10000,sigmasqinv=0.000001),
                   list(beta2=-10000,sigmasqinv=0.000001))
m2 = jags.model("hubble2.bug", data= data, inits = initial.vals, n.chains=4)

update(m2, 2000)
x2 = coda.samples(m2, c("beta2", "sigmasq"), n.iter=2000)
plot(x2, smooth = FALSE)
```

Both beta2 and sigmasq appear to be stationary. \

###*(ii)*
```{r cii}
summary(x2)
```

### *(iii)*
```{r ciii}
post.samp2 = as.matrix(x2)
mean(post.samp2[, "beta2"])
quantile(post.samp2[,"beta2"], c(0.025, 0.975))
```

### *(iv)*
```{r civ}
paste("Mean1:", mean(post.samp[,"beta2"]))
paste("Mean2:", mean(post.samp2[,"beta2"]))

paste("SD1:", sd(post.samp[,"beta2"]))
paste("SD2:", sd(post.samp2[,"beta2"]))

print("Quantile1:")
quantile(post.samp[,"beta2"])
range1= quantile(post.samp[,"beta2"])[5]-quantile(post.samp[,"beta2"])[1]
print("Quantile2:")
quantile(post.samp2[,"beta2"])
range2= quantile(post.samp2[,"beta2"])[5]-quantile(post.samp2[,"beta2"])[1]
```
Both mean slope of the no-intercept model (c) and standard deviation of slope dropped by 30 compared to those of model (b). As a result, the credible interval of model (c) also becomes narrower which is  `r range2` wide, while the credible interval fo model (b) covers `r range1`.

## *(d)*
### *(i)*
```{r di}
Nsim = dim(post.samp2)[1]
error.sim = matrix(NA, Nsim, nrow(data))
for(s in 1:Nsim){
  error.sim[s,] = (data$radialvelocity- data$distance *post.samp2[s, "beta2"])
}
```

### *(ii)*
```{r dii}
require("invgamma")
rep.y = matrix(NA, Nsim, nrow(data))
rep.normal = matrix(NA, Nsim, nrow(data))
for(i in 1:Nsim){
  rep.y[i,] = rnorm(nrow(data), data$distance*post.samp2[i, "beta2"], sqrt(post.samp2[i,"sigmasq"]))
  rep.normal[i,] = rep.y[i,]- data$distance *post.samp2[i, "beta2"]
}

```

### *(iii)*
```{r diii}
rep.test.q = abs(cor(t(rep.normal), data$distance))
test.q = abs(cor(t(error.sim), data$distance))
```

### *(iv)*
```{r div}
plot(test.q, rep.test.q, pch=".", cex=2, 
     xlim= c(min(test.q, rep.test.q), max(test.q, rep.test.q)),
     ylim = c(min(test.q, rep.test.q), max(test.q, rep.test.q)),
     xlab="cor(e,x)", ylab = "cor(rep-e, x)")
abline(a=0, b=1)
```

### *(v)*
```{r dv}
mean(rep.test.q >= test.q)
```
It seems there is no evidence of a relationship between error and distance. It suggests the no-intercept model fits.

