---
title: "Bayesian Statistics L7"
author: "kwon"
date: "2018년 9월 11일"
output: html_document
---
Two students took multiple 40 questions test, where each question has four choices.


## 1. The parameters of interest
theta1: true probability the first student will answer a question correctly /
theta2:true probability the second student will answer a question correctly /

## 2. Likelihood
Binomial(40, theta), assuming each question is independent

## 3. Prior
Conjugate prior is a beta prior.
```{r}
theta = seq(from=0, to=1, by=0.01)
plot(theta, dbeta(theta,1,1), type="l")
plot(theta, dbeta(theta,4,2), type="l")
plot(theta, dbeta(theta,8,4), type="l")

```

## 4. Prior probability
```{r}
1-pbeta(.25, 8, 4)
1-pbeta(.5, 8, 4)
1-pbeta(.8, 8, 4)

```

## 5. First student gets 33 questions right. What is posterior distirbution for theta1? P(theta1>.25)?
Beta(8+33, 4+40-33) = Beta(41, 11)
```{r}
# posterior mean
41/ (41+11)
# mle
33/40

# prior
plot(theta, dbeta(theta,8,4), type="l", ylim=c(0, 8))
# posterior
lines(theta, dbeta(theta, 44,11), lty=2)
# likelihood
lines(theta, dbinom(33, size= 40, p=theta), lty=3)
lines(theta, 44*dbinom(33, size= 40, p=theta), lty=3)
```

Posterior Probability
```{r}
1-pbeta(.25, 41, 11)
1-pbeta(.5, 41, 11)
1-pbeta(.8, 41, 11)
```

## 6. Second student gets 24 questions right, what is the posterior distiribution?
```{r}
# Beta(8+24, 4+40-24) = Beta(32,20)
32/(32+20)
24/40

# prior
plot(theta, dbeta(theta,8,4), type="l", ylim=c(0, 6))
# posterior
lines(theta, dbeta(theta, 32,20), lty=2)
# likelihood
lines(theta, 44*dbinom(24, size= 40, p=theta), lty=3)


1-pbeta(.25, 32, 20)
1-pbeta(.5, 32, 20)
1-pbeta(.8, 32, 20)
```

## 7. Estimate by simulation: draw 1000 samples from each and see how often we observe theta1 > theta2

```{r}
theta1= rbeta(1000, 41, 11)
theta2= rbeta(1000, 32, 20)
mean(theta1> theta2)
```
```{r}
plot(y, y*dgamma(y, 9, 390), type="l")
qgamma(c(0.05, 0.975), 9 ,390)

alpha=9
beta=390
y = 80:120
plot(y, dnorm(y, 96.17, 0.042), type="l")
```





















