---
title: "week3"
author: "kwon"
date: "2018년 9월 13일"
output: html_document
---

# Week3
## Hierarchical MOdel

```{r exploration}
d = read.table("rattumor.txt", header=TRUE)
head(d)
summary(d)
```
```{r histogram}
with(d, hist(y/N, freq=FALSE, xlim=c(0,1)))
```

## JAGS model specification
```{r JAGS}
require(rjags)
# d can be list or dataframe
m<- jags.model("rattumor1.bug", d)
```

```{r}
# First run it for many iteartions until it becomes reliable
# None of the samples will be used. Discard.
update(m, 2500) # burn-in

# Then run it for many more iterations, storing samples from selected nodes
x <- coda.samples(m, c("alpha", "beta"), n.iter=10000)
```
Now x is a special object containing posterior samples of $\alpha$ and $\beta$.

```{r}
head(x)

head(as.matrix(x))
```

```{r analysis}
# 2500 iterations, and 1000 adaptations
summary(x)
```
1:3500 are adpatation. \
## First block
Naive SE(Not using), Time-series SE(Standard Error for Mean): How much the approximate mean is different from true mean. \
## Second block
Represent Quantiles of variables. 50% are posterior median.

## Summary
$$ E(\alpha | y) \approx 3.4 $$
$$ \sqrt{var(\alpha|y)} \approx 1.4 $$
$$ E(\beta | y) \approx 20 $$
$$ \sqrt{var(\beta|y)} \approx 8 $$

```{r posterior density}
require(lattice)

# Posterior marginal distribution
densityplot(x)
```

```{r joint posterior distribution}
alpha =as.matrix(x)[,"alpha"]
beta =as.matrix(x)[,"beta"]
plot(alpha, beta, pch=".", cex=2)
```
The plot indicates high correlation.

```{r log sclaed graph}
plot(log(alpha/beta), log(alpha+beta), pch=".", cex=2)
```
A lot less correlation between variables.\
Were exponential hyperiors diffuse enough?\
Try different priors.


