---
title: "week 10"
author: "kwon"
date: "2018년 11월 1일"
output: pdf_document
---

# Bayesian Linear Regression
```{r setup}
Election = seq(1952, 2004, 4)
IncumbentPct = c(44.6, 57.8, 49.9, 61.3, 49.6, 61.8, 49.0, 44.7, 59.2, 53.9, 46.5, 54.7, 50.3, 51.2)
IncomeGrowth = c(2.4, 2.9, 0.8, 4.2, 3.0, 3.6, 1.1, -0.4, 3.9, 2.3, 0.4, 1.0, 2.4, 1.9)

bp = data.frame(Election, IncumbentPct, IncomeGrowth)
```
Relationship is roguly a straight line:
$$ y \approx \beta_1 + \beta_2x $$
$$ \epsilon_i = y_i - (\beta_1 + \beta_2x)$$
Epsilon considered as random, and thus, y is considered to be random.

## Conditional Modeling
y depends on X. That is, use only the conditional distribution of y given X to make inference about parameter $\theta$, ignoring masrginal distribution of X, treated as constant.

$$ \prod_{i=1}^n p(y_i|\theta, X_i) $$

$$ E(y_i | \theta, X_i) = \beta_1 x_{i1} + ... + \beta_k x_{ik} $$

Norninformative Prior
$$ p(\beta, \sigma^2 | X) \propto (\sigma^2)^{-1} $$
Still leads to proper posterior: \
- X are linearly independent \
- n > k \

Full Posterior
$$ \beta | \sigma^2, y, X \sim N(\hat \beta, \sigma^2 V_\beta$$
$$ \sigma^2 | y, X \sim Inv-\chi^2(n-k, s^2) $$

Prediction \
1. simulate $\theta = (\beta, \sigma^2)$ from poserior as before. \
2. Simulate $\hat y $ given the simulated $\theta$.

## Classical lm
```{r}
mod = lm(IncumbentPct~IncomeGrowth, data=bp)

(X = model.matrix(mod))
betahat = coef(mod)
smod=summary(mod)
s.2 = smod$sigma^2
Vbeta = smod$cov.unscaled
n.minus.k = df.residual(mod)
```

## Posterior Simulation
```{r posterior simulation}
library(MASS) # provides mvrnorm, multivariate normal
Nsim = 1000
# inverse cai square(n-k degree of freedom)
post.sigma.2.sim = n.minus.k*s.2/rchisq(Nsim, n.minus.k)

post.beta.sim = matrix(NA, Nsim, length(betahat))
# simulate beta
for(s in 1:Nsim)
  post.beta.sim[s,] = mvrnorm(1, betahat, post.sigma.2.sim[s]*Vbeta)
```

```{r}
# sigma posterior interval
quantile(post.sigma.2.sim, c(0.025, 0.975))
# beta posterior interval
apply(post.beta.sim, 2, quantile, c(0.025, 0.975))
# classical intervals, for comparison
confint(mod)
# posterior probability of the growth is positive
mean(post.beta.sim[,2] > 0)
```

## Prediction
```{r prediction}
# incomeGrowth on 2008 was 0.75
# simulate from posterior predictive distribution
post.pred.y.sim = rnorm(Nsim, post.beta.sim[,1]+post.beta.sim[,2]*0.75,sqrt(post.sigma.2.sim))

quantile(post.pred.y.sim, c(0.025, 0.975))

# classical prediction
predict(mod, data.frame(IncomeGrowth=0.75), interval="prediction")

# posterior predictive probability of 2008 incumbent victory
mean(post.pred.y.sim > 50)
```

## Diagnostics
Classical regression diagnostics are based on residuals.

## Model Checking
```{r diagnostic}
par(mfrow=c(2,2))
plot(mod)
```


## posterior-simulated standardized errors
Residuals are proxies for the errors. In bayesians, we can simulate errors from their posterior distributions.
Standardized replicated error have independent standard noraml distribution, conditional on any beta and sigma^2.
```{r}
error.std.sim = matrix(NA, Nsim, nrow(bp))
for(s in 1:Nsim)
  error.std.sim[s,] = (bp$IncumbentPct - X %*% cbind(post.beta.sim[s,])) / sqrt(post.sigma.2.sim[s])

# rnorm can be used as it is standardized and independent
ref.std.normal = matrix(rnorm(Nsim*nrow(bp)), Nsim, nrow(bp))
```

## Test quantitiy
Checking for outliers
$$ T(y, X, \theta) = \frac{max_i |\epsilon_i/\sigma|}{median_i |\epsilon_i/\sigma|} $$
```{r}
max.t.rep = apply(abs(ref.std.normal),1, max)
max.t.sim = apply(abs(error.std.sim), 1, max)
mean(max.t.rep >= max.t.sim)

median.t.rep = apply(abs(ref.std.normal), 1, max)/ apply(abs(ref.std.normal), 1, median)
median.t.sim = apply(abs(error.std.sim), 1, max)/ apply(abs(error.std.sim), 1, median)
mean(median.t.rep >= median.t.sim)
```
Stil no evidence of outliers. \

Is there any systematic relationship between errors and time t(election year)? \
consider test quantity
$$ T(y, X, \theta) = |\hat{cor}(\epsilon, t)| $$
```{r}
mean(abs(cor(t(ref.std.normal), bp$Election)) >= abs(cor(t(error.std.sim), bp$Election)))
```



