---
title: "week 7 metropolis hasting"
author: "kwon"
date: "2018년 11월 16일"
output: html_document
---
# Metropolis Hasting
```{r setup, include=FALSE}
require("coda")
```

## Random walk with normal likelihood, t prior
Total personel change in 10 companies.
Normal likelihood with known variance and t distribution for the prior on the unknown mean. \
$$ y_i | \mu \sim N(\mu, 1)$$
$$ \mu \sim t(0,1,1) $$
Thus, posterior for $\mu$:
$$ p(\mu | y_1, ..., y_n) \propto \prod_{i=1}^n[ \frac{1}{\sqrt{2\pi}} exp(-\frac{1}{2}(y_i -\mu)^2)] \frac{1}{\pi(1+\mu^2)}  $$
That is:
$$ \propto exp(-\frac{1}{2}(\sum_{i=1}^n(y_i-\mu)^2) \frac{1}{1+\mu^2} $$
$$ \propto \frac{ exp[n(\bar y\mu - \mu^2/2)]} {1+\mu^2} $$
Then, it is simplified as
$$log(g(\mu)) = n(\bar y \mu - \mu^2/2) -log(1+\mu^2) $$
where g is above function.

Ratio would be
$$ \alpha = \frac {g(\theta^*)q(\theta_{i-1} | \theta^*)}
{g(\theta_{i-1})q(\theta^* | \theta_{i-1})}
$$ 
and, for symmetric proposal distribution, q() becomes 1.

```{r}
# data
y= c(1.2,1.4, -0.5, 0.3, 0.9,2.3,1.0,0.1,1.3,1.9)

# g function
lg = function(mu, n, ybar){
  mu2 = n*(ybar*mu - mu^2/2)-log(1+mu^2)
  return(mu2)
}

# random walk metroplis hastings sampler
mh = function(n, ybar, n_iter, mu_init, cand_sd){
  
  # step 1: initailize
  mu_out = numeric(n_iter)
  accpt = 0
  mu_now = mu_init
  lg_now = lg(mu_now, n, ybar)
  
  # step 2: iterate
  for(i in 1:n_iter){
    # 2a
    mu_cand = rnorm(n=1, mu_now, cand_sd) # draw a candidate
    
    # 2b
    lg_cand = lg(mu_cand, n, ybar) # evaluate log of g with the candidate
    lalpha = lg_cand -lg_now # log of acceptance ratio, thus substracting not dividing
    alpha = exp(lalpha)
    
    # 2c
    u= runif(1)
    if(u < alpha){
      mu_now = mu_cand
      accpt = accpt+1
      lg_now = lg_cand
    }
    
    # collect results
    mu_out[i] = mu_now # save iterations' value of mu
  }
  
  return( list(mu = mu_out, accpt=accpt/n_iter))
}
```

## Visualization
```{r}
ybar = mean(y)
n = length(y)
hist(y, freq=FALSE, xlim=c(-1,3.0)) # hist of data
curve(dt(x=x, df=1), lty=2, add=TRUE) # prior
points(y, rep(0,n), pch=1) # individual data points
points(ybar, 0, pch=19)
```

## Sampling
```{r}
set.seed(5)
post = mh(n, ybar, n_iter=1e3, mu_init=0, cand_sd =3.0)
str(post)
traceplot(as.mcmc(post$mu))
post$accpt
```
It looks reached to stationary distribution. However, it appears our proposal step size is little too large`r post$accpt`
```{r}
post = mh(n=n, ybar=ybar, n_iter=1e3, mu_init=0.0, cand_sd=0.05)
post$accpt
```
This time too high.

```{r}
post = mh(n=n, ybar=ybar, n_iter=1e3, mu_init=0.0, cand_sd=0.9)
post$accpt
traceplot(as.mcmc(post$mu))
```

