---
title: "week 8 mcmc"
author: "kwon"
date: "2018년 11월 16일"
output: html_document
---

```{r setup, include=FALSE}
require(rjags)
```

# MCMC Rat tumor example
## Model
$$ y_j \sim Bin(\theta_j, n_j)$$
$$ \theta_j \sim Beta(\alpha, \beta)$$
$$ \alpha \sim Exp(\lambda=0.01) $$
$$ \beta \sim Exp(\lambda=0.01) $$


## Setting
$n_j = $ total numer of rats in contrl group of experiment j \
$y_j = $ number of control group of experiment j that develop a tumor \
$\theta_j = $ control group tumor probability in experiment j \
$$ j = 1, ..., 71 $$
- 4 chains \
- Hpyerparmeters to overdispersed \
- 1000 iterations for adaption \

- Determine crude preliminary values for parameters for "overdispersed". \
$$ \hat \theta_j = \frac {y_j}{n_j} $$ 


## JAGS
```{r}
d = read.table("rattumor.txt", header=T)
thetahat = d$y/d$N
Etheta = mean(thetahat)
Vtheta = var(thetahat)
(alphahat = Etheta*(Etheta*(1-Etheta)/Vtheta-1))
(betahat = alphahat*(1/Etheta-1))
```
To choose overdisperesed hyperparameters, it needs to 100 times larger and smaller than we expect. \
Thus, alpha ~ (0.01, 100), beta ~ (0.1, 1000)

## Initialization and adaptation
```{r}
initial.vals = list(list(alpha=0.01, beta=0.1),
                    list(alpha=100, beta=0.1),
                    list(alpha=0.01, beta=1000),
                    list(alpha=100, beta=1000))

# jags automatically conducts adaptation for default
m1 = jags.model("rattumor1.bug", d, inits = initial.vals, n.chains= 4, n.adapt = 1000)

```

```{r}
# burn-in
update(m1, 1000)
x1 = coda.samples(m1, c("alpha", "beta"), n.iter=2000)
plot(x1, smooth=FALSE)
```
4 different chains(colors) do not become converged. iterations start from 2000, because there was 1000 adaptation, and 1000 burn in.

```{r}
plot(as.matrix(x1)[,c('alpha', 'beta')], pch=".", cex=2)
```
Samples seem to have very high correlations between alpha and beta.





